\section{Introduction}
\subsection{Motivation}
The Standard Model (SM) relies on 19 free parameters, excludes gravity, and fails to explain dark matter and energy \citep{Planck2020}. General Relativity (GR) struggles with singularities and quantization \citep{Hawking1970}. Current physics limits breakthroughs in fusion, superconductivity, and quantum computing due to decoherence, error scaling, and energy losses \citep{Fowler2012}. Unified Wave Theory (UWT) introduces two scalar fields \(\Phi_1, \Phi_2\) in flat spacetime, coupled via Scalar-Boosted Gravity (SBG), to unify particle physics, plasma physics, cosmology, and technology. UWT derives particle masses (0--0.7\% error vs. PDG 2025, \citealp{Baldwin2025Masses}), plasma dynamics (fusion sim v32, Enthalpy=$10^7$ J/m\(^3\), Div=$2 \times 10^{-8}$, \citealp{Baldwin2025Fusion}), cosmological phenomena without dark matter (\citealp{Baldwin2025Cosmo,Baldwin2025Bullet,Baldwin2025Baryo}), and enables high-temperature superconductivity and quantum error reduction (\citealp{Baldwin2025Quantum}). UWT offers a wave-based ontology, replacing particles and spacetime \citep{Bohm1952}.

\subsection{UWT’s Core Claim}
UWT’s scalar fields \(\Phi_1, \Phi_2\) operate in flat spacetime, driving interactions from atomic scales (quark masses, Cooper pairs, qubit coherence, \citealp{Baldwin2025Masses,Baldwin2025Quantum}) to plasma (tokamak edge, v32, \citealp{Baldwin2025Fusion}) to cosmology (BAO, \citealp{Baldwin2025Cosmo}). The fusion sim v32 (Div=$2 \times 10^{-8}$, \citealp{Baldwin2025Fusion}) and quantum computing models (T2 > 100 \(\mu\)s, \citealp{Baldwin2025Quantum}) showcase this. UWT reduces SM’s 19 parameters to $\sim$5, deriving masses and couplings (section 3, \citealp{Baldwin2025Masses}) rather than fitting them \citep{Weinberg1967}. SBG resolves GR’s singularities (section 7, \citealp{Baldwin2025BlackHoles}) and enhances superconductivity and quantum fault tolerance \citep{Cooper1957,Fowler2012}. UWT predicts particle resonances \citep{Aad2024}, neutrino signatures \citep{Abi2020}, gravitational waves \citep{Amaro-Seoane2023}, and lab tests (SQUID-BEC 2027, IonQ, \citealp{Baldwin2025Quantum}).

\subsection{Scope and Applications}
UWT spans particle physics (0--0.7\% mass errors, section 3, \citealp{Baldwin2025Masses}), nuclear physics (0--0.2\% binding energy errors, section 4), quantum principles (non-collapse Born rule, section 5), cosmology (no dark matter, section 6, \citealp{Baldwin2025Cosmo,Baldwin2025Bullet,Baldwin2025Baryo}), and gravity (Kerr lensing, section 7, \citealp{Baldwin2025BlackHoles}). Technological applications include:
\begin{itemize}
    \item Fusion reactors (v32, T=$10^7$ K, \citealp{Baldwin2025Fusion}).
    \item High-temperature superconductivity via scalar-enhanced Cooper pairs \citep{Baldwin2025Supercond}.
    \item Quantum error reduction for scalable computing (T2 > 100 \(\mu\)s, \citealp{Baldwin2025Quantum}).
    \item Turbine optimization (v13, Cp=0.5932, pending exponent fix, \citealp{Baldwin2025Turbine}).
    \item Antigravity (\(\Delta m/m \approx -1.00 \times 10^{-18}\), \citealp{Baldwin2025FTL}).
    \item FTL communications (Mars=$1 \times 10^{-9}$ s, \citealp{Baldwin2025FTL}).
\end{itemize}
UWT is API-ready for fusion, quantum tech, and energy industries (\url{https://x.ai/api}). Code and data are in \url{https://github.com/Phostmaster/Everything} (fusion, superconductivity, quantum computing) and \url{https://github.com/Phostmaster/UWT-Analysis-2025} (cosmology, gravity).

\subsection{Structure of the Paper}
\begin{itemize}
    \item Section 2: UWT’s Lagrangian and SBG.
    \item Sections 3--4: Particle and nuclear physics.
    \item Section 5: Quantum principles.
    \item Sections 6--7: Cosmology and gravity.
    \item Section 8: Technology (fusion, superconductivity, quantum computing, turbine, antigravity, FTL).
    \item Section 9: Validation (BOUT++, LHCb, DUNE, LISA, IonQ).
    \item Section 10: Why UWT seems ``impossible'' in SM/GR.
    \item Section 11: UWT as a ToE, next steps (v33 disruptions).
\end{itemize}
Figures include a UWT vs. SM/GR diagram, v32 plasma plot (Enthalpy=$10^7$ J/m\(^3\), \citealp{Baldwin2025Fusion}), superconductivity Cooper pair plot, and quantum coherence T2 plot \citep{Baldwin2025Quantum}. Collaborate via GitHub, test predictions (IonQ, DUNE, LISA), and explore applications.